Exposing Disputed Statements on the Web

### 2009-03-23 papers/uist_thinklink/thinklink.tex
Now have a full draft

\newcommand{\want}[1]{{[\color{blue} WANT: #1]}}
\newcommand{\todo}[1]{{[\color{blue} TODO: #1]}}
\newcommand{\idea}[1]{{[\color{blue} IDEA: #1]}}

@@

\begin{figure}[tb]
	\begin{center}
	\includegraphics[width=6cm]{../screenshots/highlight_crop.png}
	\caption{Think Link highlights snippets that make disputed claims}
	\label{highlight}
	\end{center}
\end{figure}

@@

Think Link is an example of an Issue Based Information System (IBIS)~\cite{Rittel1973}. IBIS tools such as gIBIS~\cite{Conklin1987a}, Compendium~\cite{Selvin2001}, Collabatorium~\cite{Klein2007}, Zeno~\cite{Gordon1996}, and Cohere~\cite{Shum2008} model discouse as a graph of connected ideas. While the graph structure varies between tools, most tools allow one to mark an idea as supporting or opposing another idea, and allow one to mark an idea as addressing an issue. Some tools, such as Collabatorium~\cite{Klein2007} and Cope It~\cite{Karacapilidis2001} structure an argument as a tree, while others such as Think Link, gIBIS~\cite{Conklin1987a} and Cohere~\cite{Shum2008} structure an argument as a graph, in which a single idea can support or oppose multiple other ideas.

@@

In attempt to unify the different argumentation tools being developed, several interchange formats have been proposed~\cite{Rahwan2007a,McGinnis2007} to allow different web argumentation tools to share descriptions of contentious issues.

@@

Tagging Systems~\cite{Marlow2006,Golder2006} allow users to collect and organize information by associating it with an ad-hoc collection of tags. Notable tagging systems include del.icio.us\footnote{http:\\del.icio.us} which uses tags to organize web pages, and Flickr\footnote{http://flickr.com} which associates tags with photos.

@@

Some tagging and annotation tools also do clipping. Clipping tools such as Internet Scrapbook~\cite{Sugiura19998}, Hunter Gatherer~\cite{2002}, ScratchPad~\cite{Gotz2007}, ClipMarks\footnote{http://clipmarks.com}, and Diigo\footnote{http://diigo.com} allow users to collect text snippets from web pages, tag them, and share them with friends. In many cases, a tagging or clipping system will also allow users who are looking at a tagged or clipped object to see the tags that other users have associated with it, or highlight the parts of a document that have been clipped.

@@

\subsection{To discuss in the body}

Paraphrases~\cite{Chklovski2005}. Suggested formal paraphrases~\cite{Blythe2004}.
Importance of Lurkers~\cite{Takahashi2003}
Wikify~\cite{Mihalcea2007}. OpenCalais\footnote{http://opencalais.com}.

@@

Think Link uses the Wikify! algorithm~\cite{Mihalcea} to suggest topics for snippets or claims. The Wikify algorithm imagines that a piece of text was on a Wikipedia pages and predicts what pages that text would be most likely to link to, based on the probability that any particular n-gram links to any particular page. Recall that the set of Think Link topics is seeded with the set of Wikipedia page titles. The Wikify algorithm performs significantly better than a word-frequency comparison as it biases towards topics that a heavily linked to.

@@

Think Link consists of a browser extension a shared public database of contentious claims, and a web-based argument interface that allows one to explore and manipulate the claim graph. These three components are largely independent of each other and talk to each other using an open API that can also be used by other tools. Indeed the settings panel for the browser extension allows it to be pointed to alternative data stores or graphical interfaces.

As a user browses the web, the browser extension consults the database to identify snippets that other users have previously marked as making disputed claims. Any such snippets are highlighted in red to show the user that there is an alternative viewpoint that they might want to investigate. If a user clicks on a highlighted snippet then the browser extension opens the web based argument interface, showing the user the evidence that users have collected on both sides of the issue.

\todo{finish this section}

@@

We performed two qualitative ``think aloud'' user studies to guide the development of Think Link.

The aim of the first study was to see how users normally browse the web and how they might go about using Think Link to identify snippets in the pages they browse. The aim of the second study was to evaluate changes made to the interface as a result of the first study and see how people react to browsing pages that have interesting claims highlighted.

@@

Study sessions took approximately 45 minutes. Participants were seated at a single-screen workstation with the Firefox browser augmented with the Think Link plugin. We first demonstrated Think Link's interface, and then asked them to browse normally and use Think Link to identify snippets that made claims they found interesting and connect those claims to the existing claim graph. For the first half of the study, we asked them to constrain their browsing to political news articles, to increase the likelihood that there would be existing claims about the topic they were browsing.

@@

In the second study we were more confident about the usability of our tool and so we decided to tell them nothing about how to use it. We gave each user a brief introduction to the aims of the tool, similar to the introduction of this paper, and then asked them to perform two tasks with it. The first task was to look at a selection of web pages that already had highlighted snippets and explore the interface while thinking aloud about what they saw. The second task was to identify claims on a set of pages we gave them about global warming and connect them appropriately to existing claims that we had pre-populated the claim graph with. Participants were shown an interface that is largely identical to that described earlier in this paper.

@@

\subsubsection{Usability}

Several usability problems were identified with the first version of the tool, causing us to make design changes for the second version. None of these problems re-occurred during the second study. We discuss some of these changes in the sections below.

@@

\subsubsection{Creating a Snippet}

Users would often encounter a snippet that could be interpreted as making several interesting claims, and were unsure about what to do in such circumstances. Some users would deal with this by writing a compound claim like ``Global Warming will cause X and Y'' while other users would create several snippets for the same text, making different claims. Users seemed to find this confusing, suggesting that we may want support in the snippet creation interface for picking several claims that a snippet is making.

One special case of this problem was that several users wanted to mark up a table as a snippet. A table can usually be considered to be making several interesting claims and users were often confused about what they should say the table claimed. Our current guidance is that one should mark up a table as making the most interesting claims that that table makes --- those that support or oppose claims made elsewhere. In other cases, a user wanted to mark up an image as a snippet. While Think Link does not currently support this, it might make sense to allow this if an interesting claim can be inferred from the image.

Some users expressed an interest in marking up a snippet as a primary source rather than a claim. For example they might find the text of an important speech or an Olympic results table. Several expressed a desire to have a new class of object that was neither a topic nor a claim, but instead just ``interesting information relevant to this topic''.

@@

\begin{figure}[t]
	\includegraphics[width=8.5cm]{../screenshots/oldsnipcreate_diagram.png}
	\caption{Initial Prototype Snippet Creation Dialog}
	\label{oldsnippetbox}
\end{figure}

In the initial interface we used a simplified snippet creation window (Figure~\ref{oldsnippetbox}) that was intended to make the process of snippet creation very lightweight. This window contained two text boxes. The first of these boxes was for the topic (e.g. ``Global Warming'') and the second of the boxes was for the claim (e.g. ``Global Warming is Man Made''). Both of these boxes used an auto-complete drop-down list to suggest appropriate existing topics or snippets as the user typed, 
biasing towards topics that were recent or hot. The auto-complete list would show either when the user started typing, or when the user clicked the drop down button. Selecting a claim would auto-populate the topic. Selecting a topic would constrain the claims that were suggested to be within that topic.

We found that participants using this initial interface felt disorientated by the fact that the interface for creating snippets was different to the interface used for visualizing them. Participants would often confuse claims and topics, either entering a claim in the topic box, or a topic in the claim box. Participants would also frequently create new points and topics when appropriate points and topics already existed in the claim graph, even when the suggestion list was drawing their attention to a topic or claim that would have been appropriate.

For the second study, we used the snippet creation interface described earlier in this paper, which uses the same claim browser interface used for exploring the claim graph. We found that users of this interface had no difficulty distinguishing between claims and topics and were more likely to reuse existing claims and topics. We theorized that part of the reason for increased reuse was that, because users could see the claim graph they were creating, they felt more motivation to keep it ``tidy'' by reusing existing claims.

Several users expressed confusion about how specific the claim made by a snippet should be, or when they should pick an existing claim rather than create a new one. For example, if a snippet says ``Global temperatures will rise by X degrees by 2050'' then is that making the claim ``Global temperatures will rise'', or should a new claim be created that contains the extra information?

Several users also expressed an interest in being able to use the text of the snippet they selected as the text of its claim, particularly for short snippets. We intentionally made this a little difficult to do in an attempt to encourage users to find existing claims that are appropriate, however this may have been a mistake as it also increases the amount of effort required to create a snippet.

@@

Some users were confused by claims that had a ``because'' relationship rather than a ``supports'' or ``opposes'' relationship. For example ``America did not sign the Kyoto Protocol'' {\it because} ``Signing Kyoto would harm the US economy''. Similarly, many users expressed a desire to mark claims as being ``related'' without supporting or opposing each other. For example ``America did not sign the Kyoto Protocol'' {\it is related to} ``America was right to not sign the Kyoto Protocol''. Our current advice in such circumstances is to use topics to group claims that are related. For example these claims could all be in a topic called ``America and the Kyoto Protocol''. Participants seemed comfortable with the idea of relating claims in this way when we pointed it out to them, but most participants needed to be told that this was a strategy they could use.

@@

\begin{figure}[tb]
	\includegraphics[width=8.5cm]{../screenshots/oldpoint_diagram.png}
	\caption{Initial Prototype Claim Browser}
	\label{oldbrowser}
\end{figure}

\section{Limitations and Future Work}

There are a number of issues that a widely released tool would need to address. Firstly, our current implementation has privacy issues. Every time one navigates to a web page, the plugin contacts our server and gives it the current URL so that the server can check if there are snippets on that page. These requests are anonymous, cacheable, and not logged, but it is still likely that some people would object to this information being given to an external server.

At present, all claims have to be marked up by users who must not only identify the correct section of text to highlight, but also use a browsing interface to find the interesting claim that is being made. It would be interesting to see if natural language processing techniques could be used to either simplify the process of marking snippets, or even to detect snippets that make known claims without human intervention.

@@

We have introduced the concept of browsing the web of factual claims using Think Link. Think Link allows users to navigate between pages based on the factual claims made on pages, rather than being restricted to the links provided by authors. It allows users to identify contentious claims on web pages and connect them directly to the arguments that those claims are part of, and related claims on other web sites.

On a practical level, Think Link works by allowing users to pick out snippets on pages that make claims that they think are interesting or controversial, and then using an ``append only, collaborative filtering'' model to allow users to collaborate together to structure claims into an argument graph.

@@

We would like to think Allison Woodruff, Tye Rattenbury, and all our user study participants for all their help during the design of Think Link. Think Link uses icons from the free FamFamFam Silk\footnote{http:\\famfamfam.com} collection.

>>>>

% \newcommand{\want}[1]{{[\color{blue} WANT: #1]}}
% \newcommand{\todo}[1]{{[\color{blue} TODO: #1]}}
% \newcommand{\idea}[1]{{[\color{blue} IDEA: #1]}}
% \newcommand{\node}[1]{{[\color{blue} NOTE: #1]}}

\newcommand{\want}[1]{}
\newcommand{\todo}[1]{}
\newcommand{\idea}[1]{}
\newcommand{\node}[1]{}

@@

\begin{figure}[tb]
	\begin{center}
	\includegraphics[width=5cm]{../screenshots/highlight_crop.png}
	\caption{Think Link highlights snippets that make disputed claims}
	\label{highlight}
	\end{center}
\end{figure}

@@

Think Link is an example of an Issue Based Information System (IBIS)~\cite{Rittel1973}. IBIS tools such as gIBIS~\cite{Conklin1987a}, Compendium~\cite{Selvin2001}, Collabatorium~\cite{Klein2007}, Zeno~\cite{Gordon1997}, and Cohere~\cite{Shum2008} model discouse as a graph of connected ideas. While the graph structure varies between tools, most tools allow one to mark an idea as supporting or opposing another idea, and allow one to mark an idea as addressing an issue. Some tools, such as Collabatorium~\cite{Klein2007} and Cope It~\cite{Karacapilidis2001} structure an argument as a tree, while others such as Think Link, gIBIS~\cite{Conklin1987a} and Cohere~\cite{Shum2008} structure an argument as a graph, in which a single idea can support or oppose multiple other ideas.

@@

@@

Tagging Systems~\cite{Marlow2006,Golder2006} allow users to collect and organize information by associating it with an ad-hoc collection of tags. Notable tagging systems include del.icio.us\footnote{http://del.icio.us} which uses tags to organize web pages, and Flickr\footnote{http://flickr.com} which associates tags with photos.

@@

Some tagging and annotation tools also do clipping. Clipping tools such as Internet Scrapbook~\cite{Sugiura1998}, Hunter Gatherer~\cite{Schraefel2002}, ScratchPad~\cite{Gotz2007}, ClipMarks\footnote{http://clipmarks.com}, and Diigo\footnote{http://diigo.com} allow users to collect text snippets from web pages, tag them, and share them with friends. In many cases, a tagging or clipping system will also allow users who are looking at a tagged or clipped object to see the tags that other users have associated with it, or highlight the parts of a document that have been clipped.

@@

% \subsection{To discuss in the body}
% 
% Paraphrases~\cite{Chklovski2005}. Suggested formal paraphrases~\cite{Blythe2004}.
% Importance of Lurkers~\cite{Takahashi2003}
% Wikify~\cite{Mihalcea2007}. OpenCalais\footnote{http://opencalais.com}.

@@

Think Link uses the Wikify! algorithm~\cite{Mihalcea2007} to suggest topics for snippets or claims. The Wikify algorithm imagines that a piece of text was on a Wikipedia pages and predicts what pages that text would be most likely to link to, based on the probability that any particular n-gram links to any particular page. Recall that the set of Think Link topics is seeded with the set of Wikipedia page titles. The Wikify algorithm performs significantly better than a word-frequency comparison as it biases towards topics that a heavily linked to.

@@

Think Link consists of a browser extension, a page annotation script, a shared public database of contentious claims, and a web-based argument interface that allows one to explore and manipulate the claim graph. These four components are largely independent of each other and talk to each other using an open API that can also be used by other tools. Indeed the settings panel for the browser extension allows a user to tell it to bind to alternative versions of the other modules.

The page annotation script is a javascript file that can be included into any HTML page. When it is run on a page it sends the page URL to the server, asking it to send back information about any contentious snippets on that page. If any such snippets are found, the page modification script highlights them in red. If the user clicks on a highlighted snippet then it shows an iframe containing a visualisation from whatever visualization server it has been configured to use.

The only purpose of the browser extension is to insert the page modification script onto every page that the user loads. The browser extension is not the only way that one can access Think Link highlights. One can get the same effect by browsing through a proxy (like WBI~\cite{Barrett1997}), or if the owner of a web site included the page annotation script themselves.

Think Link's annotation system has some privacy issues. Every time the user browses to a page, the URL is sent to the Think Link server to check whether there are any known annotations for that page. Privacy issues are reduced by the fact that the requests contain no cookies or other identifying information, and can be cached by a third-party proxy if desired; however issues still remain. In future work hope to reduce these privacy issues. One possibility is to use a hashing system similar to that used by Google Safe Browsing\footnote{http://code.google.com/p/google-safe-browsing/}.

The protocol used by the Think Link server is an open REST API that other tools are free to use. We are also considering supporting one or more of the several argumentation interchange formats that have been proposed ~\cite{Rahwan2007a,McGinnis2007}.

@@

We performed two qualitative ``think aloud'' user studies. The aim of these studies was to inform the development of Think Link. The studies were not intended to validate the design of Think Link as being correct. Think Link is designed to be used by a large number of users gathering a vast amount of evidence for many different points. To confidently state that our design was successful we would need to be able to test Think Link on a much greater scale than we currently have resources for.

The aim of the first study was to see how users normally browse the web and see their reactions to an early version of the Think Link argument graph. The aim of the second study was to evaluate user responses to an updated version of the interface and evaluate how users responded to seeing highlighted snippets on the page. We present the results of the two studies together.

@@

\todo{This was a bad recruiting strategy. We should have recruited people that fitted one of our two personas and then set them tasks that fitted our vision for that persona.}

Study sessions took approximately 45 minutes. Participants were seated at a single-screen workstation with the Firefox browser augmented with the Think Link extension. We first demonstrated Think Link's interface, and then asked them to browse normally and use Think Link to identify snippets that made claims they thought were interesting or disputed and connect those claims to the existing claim graph. For the first half of the study, we asked them to constrain their browsing to political news articles, to increase the likelihood that there would be existing claims about the topic they were browsing.

@@

In the second study we were more confident about the usability of our tool and so we decided to tell them nothing about how to use it. We gave each user a brief introduction to the aims of the tool, similar to the introduction of this paper, and then asked them to perform two tasks with it. The first task was to look at a selection of web pages that already had highlighted snippets and explore the interface while thinking aloud about what they saw (the ``sceptical reader'' use case). The second task was to identify disputed claims on a set of pages we gave them about global warming and connect them appropriately to existing claims that we had pre-populated the claim graph with (the ``activist'' use case).

Participants were shown the prototype interface shown in Figure~\ref{secondbrowser}. This is similar to the interface described earlier in this paper, but uses drag and drop to make connections, rather than a suggestion system.

@@

@@

\begin{figure}[t]
	\includegraphics[width=8.5cm]{../screenshots/oldsnipcreate_diagram.png}
	\caption{First Prototype Snippet Creation Dialog}
	\label{oldsnippetbox}
\end{figure}

\begin{figure}[t]
\begin{center}
	\includegraphics[width=5cm]{../screenshots/newsnip_browseopen.png}
	\caption{Second Prototype Snippet Creation Dialog}
	\label{secondsnippetbox}
\end{center}
\end{figure}

The prototype interfaces required that a user enter a claim for a snippet at the point at which they created the snippet. When the user marked a snippet, Think Link would display a dialog box asking them what claim to associate it with (Figure~\ref{oldsnippetbox} for the first prototype and Figure~\ref{secondsnippetbox} for the second prototype). There turned out to be several problems with requiring that a user select a claim at the point at which they marked a snippet:

Users would often encounter a snippet that could be interpreted as making several interesting claims. Users got confused by the need to pick only one claim. Some users dealt with this by writing a compound claim such as ``Global warming will cause X and Y'', while other users would mark several overlapping snippets making different claims. In the final interface one can associate a snippet with several claims.

Some users wanted to associate a snippet with a topic but without associating it with a specific claim. For example, they might find the text of an important speech, or the results of a sporting event. While it is possible that they might want to use this as evidence for a claim in the future, they didn't want to have to decide what the claim was immediately. In the final interface one can associate a snippet with a topic rather than a claim.

Some users seemed to be deterred from marking interesting snippets by the mental effort required to choose an appropriate claim. In several cases, we saw a user pause to decide whether an interesting snippet was worth marking up. Similarly, some users seemed to find it difficult to decide what the right claim to use for a snippet was, since they had not yet decided how they wanted to structure their argument, or even if this was a topic they wanted to argue about. The final interface does not require a user to associate a snippet with a claim at the time they create the snippet. Instead a user can mark snippets with minimal effort and then later search through their snippets to find evidence for particular claims.

Several users expressed confusion about how specific the claim made by a snippet should be, or when they should pick an existing claim rather than create a new one. For example, if a snippet says ``Global temperatures will rise by X degrees by 2050'' then is that making the claim ``Global temperatures will rise'', or should a new claim be created that contains the extra information? In the final interface, users can choose how specific to make their claims after they have gathered a large number of snippets and know what information is repeated between sources.

Since a user was required to enter a claim whenever they created a snippet, there was an incentive for the user to enter a claim as quickly as possible so they they could make the dialog go away. Several users created a new claim that was equivalent to a claim that already existed, and several users repeatedly created a claim that had the exact same text as the snippet. The final interface avoids this problem by allowing a used to delay the association of a claim for a snippet until they know what useful claim they want to use that snippet as evidence for.

\todo{Need to do some kind of evaluation to show that the new interface solves these problems}

\subsubsection{Choosing what to mark as a snipet}

@@

Several users wanted to mark up a table or an image as a snippet. This is valid behaviour -- a table or image is often useful evidence for a claim; however it is not currently supported by Think Link. In future versions of Think Link we intend to support this behaviour.

@@

Some users were confused by claims that had a ``because'' relationship rather than a ``supports'' or ``opposes'' relationship. For example ``America did not sign the Kyoto Protocol'' {\it because} ``Signing Kyoto would harm the US economy''. Similarly, many users expressed a desire to mark claims as being ``related'' without supporting or opposing each other. For example ``America did not sign the Kyoto Protocol'' {\it is related to} ``America was right to not sign the Kyoto Protocol''. In the first prototypes, a user needed to chose between ``supports/opposes'' when connecting two claims together (follwing gIBIS~\cite{Conklin1987a}). In the final interface we introduced a ``related-to'' link type to allow users to connect claims that they thought should be related but which didn't confirm to a simple pro/con relationship.

@@

\begin{figure}[tb]
	\includegraphics[width=8.5cm]{../screenshots/oldpoint_diagram.png}
	\caption{First Prototype Claim Browser}
	\label{oldbrowser}
\end{figure}

\begin{figure}[tb]
\begin{center}
	\includegraphics[width=5cm]{../screenshots/claimbrowse.png}
	\caption{Second Prototype Claim Browser}
	\label{secondbrowser}
\end{center}
\end{figure}

The first two versions of Think Link used a drag-and-drop interface to allow a user to create links between claims. In the first interface (Figure~\ref{oldbrowser}) a user could use a search box to find other claims and then drag them into an appropriate position in the argument tree. In the second interface (Figure~\ref{secondbrowser}), followed a file-manager metaphore, providing two identical browser windows that a user could drag and drop claims between. In both cases, we found that users would often not intially realise they could use drag and drop to arganize claims, even when we added a prominant information message at the top of the display (Figure~\ref{secondbrowser}). We believe that part of the problem was that users are not used to using drag-and-drop in a web interface, and there was no visible clue in the rendering of the claim graph that they could use drag and drop to create connections. In the final interface we resolved this issue by having the connection actions (``add claim'' etc) explicitly visible in the interface.

\section{Future Work}

At present Think Link relies on users to mark up snippets and connect them to claims. In the future we plan to explore using natural language and machine learning techniques to assist in this process. Our plan is to allow a user to request that Think Link present them with potential web snippets that make a claim that they disagree with, and then quickly select which of these should be highlighted as being contentious.

@@

We have introduced the idea of enhancing the browsing interface by highlighting snippets of text that make disputed claims and allowing a user to see an argument graph that presents the best evidence on either side of the issue. Think Link allows users to navigate between pages based on the factual claims made on pages, rather than being restricted to the links provided by authors. It allows users to identify disputed claims on web pages and connect them directly to the arguments that those claims are part of, and related claims on other web sites.

On a practical level, Think Link works by allowing users to pick out snippets on pages that make claims that they think are interesting or controversial, and then using a collaborative filtering model to allow users to vote for the most interesting evidence and structure claims into a coherent argument graph.

@@

Acknowledgements ommitted for blind submission. Think Link uses icons from the free FamFamFam Silk\footnote{http:\\famfamfam.com} collection.
